Transcriptomics Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-06-11 Cover_letter_JPM.tex
Updates from Overleaf

\subsection*{2-1}%(ok)
% sliding window cutoff selection with FDR corrected
Exploring all possible expression cutoffs is controversial. 
A robust expression biomarker should be effective and detectable at most major cutoffs. Compared to a fixed quantile cutoff, a sliding window cutoff selection of cutoffs would capture more genes whose p-values just reach the significant level (p=0.05). 
For example, a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 0.04 at 70\% quantile cutoff. % might be false positive
But it is not expected that a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 1e-5 at 70\% quantile cutoff. % true positive
This strategy only identifies more weak “biomarkers,” and it also captures more false positives. % => NOT weak 其實 very significant
Adjustment of multiple test p-values should be applied here, which is missing in the current manuscript.
% PPV positive prediction value => prevalence-sensitive (COVID-19 盛行率的觀念一致) ROC from sensitivity and specificity

@@

% 1) ***We modified the workflow as ...(本來就有計算 FDR and excluding >= 0.05)
% 2) and FDR (done)
We appreciate the reviewer to kindly advise us about the principle of sliding window cutoff selection in detail.
% and give us this nomenclature as "sliding window"
%% *** 準備一張 20 candidates: accumulated \textit{P}-value plots 來說明，其實這些 P values 不論 50% cut or 70% 幾乎都 far less than 0.05
We correct our statement of this workflow (please see Answer 2-2).
There is more evidence to validate them (please see Answer 2-3).

@@

% strategy should changing; run GCP Rstudio 框列更多的 candidates for GEO validation
In the independent test, half genes have p-values less than 0.05, and most of them have p-values $> 0.01$. % table 1 => this is Bonferroni 的結果
Purely based on the number of genes and their p-values, the validation rate is relatively low, and the usability of the biomarkers is questionable. % the validation rate 
The p-values are affected by the sample size, which should be described in the main text. % writing
As I mentioned above, the authors should look for more data to verify these biomarkers. % GEO

@@

%%%
For validation by GEO datasets:

% National Center for Biotechnology Information Reference Sequence (NCBI) RefSeq Release 38 (November 7, 2009)

GEOquery\cite{Sean2007}: SOFT file (or MINiML)
the NCBI GEO repositories
%https://warwick.ac.uk/fac/sci/moac/people/students/peter_cock/r/geo/
*the authors should look for more data to verify these biomarkers.
by TMA IHC of HNSCC (provided by Prof. Michael Hsiao)
or CPTAC (digital TMA, not HPA)i

or more GEO datasets (*GEO2837, GSE40774, ***GSE65858, *GSE117973, GSE148944, and GSE41613/xGSE42743)
* GSE2837 https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837

*** https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE65858 GSE65858
https://onlinelibrary.wiley.com/doi/full/10.1002/ijc.29649
OS event and RFS event and survival time
n=270\cite{Wichmann2015}
Each array on the HumanHT-12 v4 Expression BeadChip targets more than 31,000 annotated genes with more than 47,000 probes derived from the \acrfull{ncbi} Reference Sequence (RefSeq) Release 38 (November 7, 2009) and other sources.
% https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GPL10558

@@

>>>>

\subsection*{2-1}%(ok)
% sliding window cutoff selection with FDR corrected
Exploring all possible expression cutoffs is controversial. 
A robust expression biomarker should be effective and detectable at most major cutoffs. Compared to a fixed quantile cutoff, a sliding window cutoff selection of cutoffs would capture more genes whose p-values just reach the significant level (p=0.05). 
For example, a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 0.04 at 70\% quantile cutoff. % might be false positive
But it is not expected that a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 1e-5 at 70\% quantile cutoff. % true positive
This strategy only identifies more weak “biomarkers,” and it also captures more false positives. % defense (ok) => NOT weak 其實 very significant; 欠一張圖
Adjustment of multiple test p-values should be applied here, which is missing in the current manuscript.
% (ok) PPV positive prediction value => prevalence-sensitive (COVID-19 盛行率的觀念一致) ROC from sensitivity and specificity

@@

% 1) 本來就有計算 FDR and excluding >= 0.05 (ok)
% 2) and FDR (done)
We appreciate the reviewer to kindly advise us about the principle of sliding window cutoff selection in detail.
% and give us this nomenclature as "sliding window"
%% *** 準備一張 20 candidates: accumulated \textit{P}-value plots 來說明，其實這些 P values 不論 50% cut or 70% 幾乎都 far less than 0.05
We correct our statement of this workflow (please see Answer 2-2).
There is more evidence to validate them (please see Answer 2-3).

We understand that the sliding-window selection of cutoffs would capture more genes whose \textit{P} values just reach the significant level (p=0.05).
*** According to our results, all of preliminary biomarkers have FDR-corrected \textit{P} values from 1e-4 to 0.04 whatever grouped by cutoffs at 50\% quantile cutoff or at 70\% quantile cutoff (Please see supplementary Figure SXXX).
There is so many thing we could find during the data mining from so many 20500 protein-coding genes.
Thus we also performed the FDR correction applied on cutoff finding procedure as well as Bonferroni adjustment in candidate filtering.

@@

% strategy should changing; run GCP Rstudio 框列更多的 candidates for GEO (GSE65858) validation
In the independent test, half genes have p-values less than 0.05, and most of them have p-values $> 0.01$. % table 1 => this is Bonferroni 的結果
Purely based on the number of genes and their p-values, the validation rate is relatively low, and the usability of the biomarkers is questionable. % the validation rate 
The p-values are affected by the sample size, which should be described in the main text. % writing
As I mentioned above, the authors should look for more data to verify these biomarkers. % GEO

@@

%%%
*the authors should look for more data to verify these biomarkers.
For validation by GEO datasets:

% 
National Center for Biotechnology Information Reference Sequence (NCBI) 
%RefSeq Release 38 (November 7, 2009) 
Gene Expression Omnibus (GEO)
[Dataset]
The NCBI GEO repositories is a public repository supporting MIAME-compliant data submissions of microarray and sequence-based experiments.
R package of GEOquery\cite{Sean2007}: SOFT file (or MINiML) was used to
download RNA-Seq dataset of HNSCC, GSE65858, from the GEO database (available at https://www.ncbi.nlm.nih.gov/geo/geo2r/?acc=GSE65858). 
GSE65858\cite{Wichmann2015} has OS event and RFS event and survival time.
%n=270 n= 273 = ?? + 168(alive) + 88(dead) = 256
The expression data was generated using the HumanHT-12 v4 Expression BeadChip, which targets on more than 31,000 annotated genes (47,000 probes) derived from the \acrfull{ncbi} Reference Sequence (RefSeq) Release 38 (November 7, 2009).
% an Affymetrix Human Genome U133A microarray (HG-U133A). 
It was used as a validation dataset.

%https://warwick.ac.uk/fac/sci/moac/people/students/peter_cock/r/geo/

by TMA IHC of HNSCC (provided by Prof. Michael Hsiao)
or CPTAC (digital TMA, not HPA)i

or more GEO datasets (*GEO2837, GSE40774, ***GSE65858, **GSE117973, GSE148944, and GSE41613/xGSE42743)
* GSE2837 https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837

*** https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE65858 GSE65858
https://onlinelibrary.wiley.com/doi/full/10.1002/ijc.29649
% https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GPL10558

@@

***
Third, dissection of ZSWIM2\_archive.Rda % 其實最困難的在於 unknown error (ZSWIM2) due to heterogeneity of 20500 RNA-Seq expression data files.
